Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Edit algorithm performance text

We assign an exponential density (Eq.~\ref{eq:density-exp}) with values of $b$ equal to
1, 2, 5, 10, 30 and 100, and a sinusoidal density (Eq.~\ref{eq:density-sine}) with
values of $b$ equal to 1, 2, 5, and 10 to an arbitrary tesseroid.
Then we applied the density-based discretization algorithm on each case recording how
many subdivisions it carried out and where the boundaries of the smaller tesseroids are
located.
On both exponential and sinusoidal density cases a value of $\delta$ equal to 0.1 has
been used.

Figs.~\ref{fig:number-of-tesseroids}(a) and~\ref{fig:number-of-tesseroids}(b) show the
exponential and sinusoidal densities used and the resulting boundaries of the
discretized tesseroids as orange dots.
The number of discretizations are independent of the value of factor $b$ in the
exponential density case: the algorithm only performs one split independently of $b$.
On the other hand, the sinusoidal density results show a significant relation between
the number of discretizations and the constant $b$.
Fig.~\ref{fig:number-of-tesseroids} shows an almost linear relation between these two
magnitudes.

Therefore, the computation time for the exponential density would be increased in
comparison to the homogeneous density case because the
single split the density-based algorithm performs, although it will be independent of
the value of $b$.
On the other hand, the computation time for the sinusoidal density is bounded to the
value of $b$ used, greatly increasing it for a large $b$ as 100.

>>>>

We assign an exponential density (Eq.~\ref{eq:density-exp}) with values of $b$ equal to
1, 2, 5, 10, 30 and 100, and a sinusoidal density (Eq.~\ref{eq:density-sine}) with
values of $b$ equal to 1, 2, 5, and 10 to an arbitrary tesseroid.
Then we applied the density-based discretization algorithm on each case recording how
many subdivisions it carried out and where the boundaries of the smaller tesseroids are
located.
Figs.~\ref{fig:number-of-tesseroids}(a) and~\ref{fig:number-of-tesseroids}(b) show the
exponential and sinusoidal densities used and the resulting boundaries of the
discretized tesseroids as orange dots.
On both exponential and sinusoidal density cases a value of $\delta$ equal to 0.1 has
been used.

On the exponential density scenario, the algorithm performs a single split independently
of the value of $b$, i.e.~the number of discretizations is independent of the
variability of the exponential function.
Therefore, the computation time would be increased in comparison to the homogeneous
density case due to this single split, but would be independent of the value of $b$.

On the other hand, the sinusoidal density case shows a strong dependence of the
number of discretizations on the value of $b$.
Fig.~\ref{fig:number-of-tesseroids} shows an almost linear relation between these two
magnitudes.
This means that the computation time is heavily bounded to the value of $b$ used.
It can be greatly increased for large values of $b$ such as 100.

From this results we can conclude that the computation time would be greatly increased
in case of multiple inflection points on the density function.
Nevertheless, for most geophysical applications on which the density profiles may have
low number of inflection points, the computation time would be in the same order of
magnitude as the one for the homogeneous density case.
